---
title: "Empirical Bayes Estimators for Population-Specific Association"
author: "Li Hsu, Lilian Law"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

ebest provides joint and pairwise empirical Bayes (EB) estimators for population-specific association analysis, 
while leveraging information from other populations, accounting for both the uncertainty of the estimates and 
heterogeneity across populations. ebest also provides the conventional meta-analysis fixed effect estimator 
for combining the estimates across populations.

Multiple R packages are called in ebest and if possible should be installed beforehand. These packages are: 

- quadprog
- tibble

The main function to used for examples and in the ebest package is the function ebest. The required inputs are:

- K: Number of populations
- betas: Vector of regression coefficient estimates for the K populations, the first one is considered as the population of interest
- ses: Vector of standard errors of the corresponding regression coefficient estimates for the \emph{K} populations

References for the methods used: 

- Hsu, L., Kooperberg, A., Reiner, A.P. and Kooperberg, C., (2023) An empirical Bayes approach to improving population‐specific genetic association estimation by leveraging cross‐population data. Genetic Epidemiology, 47(1), pp.45-60.

The following is an example of the ebest function contained in the ebest package

```{r}
library(ebest)
K=3      # number of populations
est = c(0.1, 0.2, 0.3)   # parameter estimates of the three populations, with the first population being of the primary interest
se = c(0.2, 0.2, 0.2)   # standard errors of parameter estimates
ebest(K=K, betas= est, ses = se)
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
